Manuscript for MADA Project

### 2023-04-10 products/Manuscript.qmd
Part 4

---
title: "Manuscript for MADA Project"
subtitle: ""
author: Jacob Matta
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../My_Library.bib
csl: ../apa.csl
---

@@

The data is a count of residents with at least one COVID-19 vaccination by demographic in the state of Georgia released by the Georgia Department of Public Health. The data has 1962 observations which are 1962 different census tracts in Georgia. There are 187 variables each are a different combination of gender, race and age. The data is uploaded weekly.

@@

In preparation for analysis, the raw data was first sub-setted by  Dougherty County, the county in which Albany, Georgia lies. This allowed me to work only with census tracts from Dougherty county. I then summed the data by demographic to get demographic totals

@@

>>>>

---
title: "Manuscript for MADA Project"
subtitle: ""
author: Jacob Matta
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ./My_Library.bib
csl: ./apa.csl
---

@@

The data is a count of residents with at least one COVID-19 vaccination by demographic in the state of Georgia released by the Georgia Department of Public Health. The data has 1962 observations which are 1962 different census tracts in Georgia. There are 187 variables each are a different combination of gender, race and age. The data is uploaded monthly.

@@

In preparation for analysis, the raw data was first sub-setted by  Dougherty County, the county in which Albany, Georgia lies. This allowed me to work only with census tracts from Dougherty county. I then summed the data by demographic to get demographic totals.

@@

## Vaccination Trends of the Black Community for Each Zip Code 
```{r}
knitr::include_graphics("../results/31701_total_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31705_total_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31707_total_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30815_total_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30907_total_black_vax.png")
```

## Vaccination Trends of the Black Community for Each Zip Code by Gender
```{r}
knitr::include_graphics("../results/31701_Gender_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31705_Gender_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31707_Gender_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30815_Gender_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30907_Gender_black_vax.png")
```

## Vaccination Trends of the Black Community for Each Zip Code by Gender
```{r}
knitr::include_graphics("../results/31701_Age_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31705_Age_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31707_Age_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30815_Age_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30907_Age_black_vax.png")
```

## LASSO Results Visual 
```{r}
knitr::include_graphics("../results/lasso_grid_plot.png")
```

## Final LASSO Results Variable Importance 
```{r}
knitr::include_graphics("../results/final_lasso_plot.png")
```

### 2023-04-10 products/supplement.qmd
Part 4

        -   `processingcode1.qmd`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in September 2022

        -   `processingcode1.R`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in September 2022

        -   `processingcode2.qmd`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in October 2022

        -   `processingcode2.R`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in October 2022

        -   `processingcode3.qmd`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in November 2022

        -   `processingcode3.R`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in October 2022

        -   `processingcode4.qmd`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in December 2022

        -   `processingcode4.R`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in December 2022

        -   `processingcode5.qmd`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in January 2023

        -   `processingcode5.R`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in January 2022

        -   `processingcode6.qmd`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in February 2023

        -   `processingcode6.R`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in February 2023

@@

        -   `analysiscode1.qmd`: Contains the code an analysis of the total amount of African Americans with at least one COVID-19 vaccine in all three target zip codes
        -   `analysiscode1.html`: Contains the output document from rendering `analysiscode1.qmd`
        -   `readme.md`: provides a brief description of the analysis files

@@

-   `results` folder: Contains the graphs produced from rendering the analysis `analysiscode1.qmd`

>>>>

        -   `processingcode.qmd`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in September 2022

@@

        -   `exploratoryanalysis.qmd`: Contains the code to an analysis of the total amount of African Americans with at least one COVID-19 vaccine in all three target zip codes and two control zip codes

        -   `statisticalanalysis.qmd`: Contains the code to a statistical analysis of the total amount of African Americans with at least one COVID-19 vaccine in all three target zip codes and two control zip codes

        -   `readme.md`: provides a brief description of the analysis files

@@

-   `results` folder: Contains the graphs produced from rendering the analysis
